\thispagestyle{plain}			% Supress header
\section*{Terminology}
\subsection*{General terms and abbreviations}
\begin{description}[style=nextline]
  \item[ABI] Application binary interface. A machine-level entry point for a program component.
  \item[API] Application programming interface. A high-level entry point to a software component.
  \item[Bitcoin] Short for the Bitcoin network. For the currency used by the network, see \emph{BTC}.
  \item[Blockchain] A distributed and decentralized data store.
  \item[BTC] (pronounced as Bitcoin) refers to the currency in the Bitcoin network.
  \item[Centralized system] A system with one or more central points.
  \item[Cryptographic hash] A definite one way hash function.
  \item[DDoS] Distributed denial of service attack.
  \item[Decentralized system] A system without any central points.
  \item[Ether] The currency of the Ethereum network. Compare with BTC and Bitcoin.
  \item[Ethereum] A general-purpose blockchain network.
  \item[JSON] JavaScript object notation.
  \item[JSON-RPC] A JSON-based remote procedure call scheme.
  \item[MITM-attack] Man-in-the-middle--attack. An attack where one relays, and possibly modifies, communication between two nodes who believe they are directly communicating to each other.
  % https://www.owasp.org/index.php/Man-in-the-middle_attack
  \item[Nonce] An arbitrary number used only once in a certain (cryptographic) environment.
  \item[Peer-to-peer network] A network in which the nodes communicate directly with each other. 
  \item[Proof-of-work] Regulatory mechanism in a blockchain designed to deter forgery.
  \item[REST(ful)] Representational state transfer. An API model.
  \item[Smart contract] A piece of deterministic code, run on a blockchain, with which various entities can interact.
  \item[Trustless] Literally without trust. Here meant to signify that no trust is neccessary between nodes in the network.
  \item[Whisper] An anonymous message passing service on the Ethereum network.
  
\end{description}
%\newpage

\subsection*{Terms with specific meanings in the thesis}
\begin{description}[style=nextline]
  \item[Client] A user paying to perform \textit{work} on the cloud platform.
  \item[Verifier] A \textit{worker} that verifies other workers.
  \item[Work] An arbitrary piece of software to be run by a \textit{worker}, at the behest of a \textit{client}.
  \item[Worker] A cloud platform node performing \textit{work} in exchange of monetary compensation.
\end{description}

%\newpage				% Create empty back of side
%\thispagestyle{empty}
%\mbox{}
